Distributional Regression Forests for Probabilistic Modeling and Forecasting

### 2018-02-09 pkg/disttree/inst/Psychoco2018/slides.Rnw
revisions: flow
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2002 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: aefa79f5043688378d3cd846b6a686e55bfe60d3

\documentclass[11pt,t,usepdftitle=false,aspectratio=43]{beamer}
\usetheme[nototalframenumber, noslidenumber]{uibk}

\title{Distributional Trees and Forests}
\author{Lisa Schlosser, Torsten Hothorn,\\ Heidi Seibold, Achim Zeileis}
\setbeamerfont{url}{size*={11.5pt}{13pt},series=\mdseries}
\URL{https://R-Forge.R-project.org/projects/partykit/}
\headerimage{3}

@@

\begin{frame}[fragile]
\frametitle{Motivation}
\vspace{-0.41cm}
\begin{figure}[!htb]
\minipage{0.29\textwidth}
\begin{center}
<<motivation_GLM, echo=FALSE, results=hide>>=
nobs <- 200
## GLM
set.seed(7)
x <- c(1:nobs)/nobs
ytrue <- 1+x*1.5
y <- ytrue + rnorm(nobs,0,0.3)
@
\visible<2->{
<<plot_motivation_GLM, fig=TRUE, echo=FALSE>>=
par(mar=c(2,0,2,0))
plot(y=y , x=x, xaxt="n", yaxt="n", ann=FALSE, col = "slategray", pch = 19)
box(lwd=5)
lines(x = x, y = ytrue, col = pal["forest"], lwd = 7, main = "")
@
}
\end{center}
\endminipage
\visible<3->{{\LARGE$\rightarrow$}}
\minipage{0.29\textwidth}
\begin{center}
<<motivation_GAM, echo=FALSE, results=hide>>=
## GAM
set.seed(7)
x <- c(1:nobs)/nobs
x <- 2*(x-0.5)
ytrue <- x^3 
y <- ytrue + rnorm(nobs,0,0.3)
@
\visible<3->{
<<plot_motivation_GAM, fig=TRUE, echo=FALSE>>=
par(mar=c(2,0,2,0))
plot(y=y , x=x, xaxt="n", yaxt="n", ann=FALSE, col = "slategray", pch = 19)
box(lwd=5)
lines(x = x, y = ytrue, col = pal["forest"], lwd = 7, main = "")
@
}
\end{center}
\endminipage
\visible<4->{{\LARGE$\rightarrow$}}
\minipage{0.29\textwidth}
\begin{center}
<<motivation_GAMLSS, echo=FALSE, results=hide>>=
## GAMLSS
set.seed(7)
x <- c(1:nobs)/nobs
x <- 2*(x-0.5)
ytrue <- x^3
var <- exp(-(2*x)^2)/2
y <- ytrue + rnorm(nobs, 0, 0.1 + var)
@
\visible<4->{
<<plot_motivation_GAMLSS, fig=TRUE, echo=FALSE>>=
par(mar=c(2,0,2,0))
plot(x, y, xaxt = "n", yaxt = "n", ann = FALSE, type = "n")
polygon(c(x, rev(x)), c(ytrue + 0.1 + var, rev(ytrue - 0.1 - var)),
  col = pallight["forest"], border = "transparent")
lines(x, ytrue, col = pal["forest"], lwd=7)
points(x, y, col = "slategray", pch = 19)
box(lwd = 5)
@

@@

\begin{frame}[fragile]
\frametitle{Motivation}
\vspace{-0.2cm}
\begin{figure}[!htb]
\minipage{0.29\textwidth}
\begin{center}
<<motivation_regtree, echo=FALSE, results=hide>>=
## Reg. Tree
set.seed(7)
kappa <- 12
x <- c(1:nobs)/nobs
ytrue <- ytree <- yforest <- numeric(length = length(x))
for(i in 1:nobs) ytrue[i] <- if(x[i]<1/3) 0.5 else 1+(1-plogis(kappa*(2*(x[i]-0.2)-1)))
y <- ytrue + rnorm(nobs,0,0.3)
for(i in 1:nobs) ytree[i] <- if(x[i]<1/3) 0.5 else {if(x[i]<2/3) 2 else 1}
@
\visible<1->{
<<plot_motivation_regtree, fig=TRUE, echo=FALSE>>=
par(mar=c(2,0,2,0))
plot(x = x, y = y, xaxt="n", yaxt="n", ann=FALSE, col = "slategray", pch = 19)
box(lwd=5)
#lines(x = x, y = ytrue, col = "grey", lwd=5, main = "")
lines(x = x, y = ytree, col = pal["forest"], lwd=7)
@
}
\end{center}

\endminipage
\visible<2->{{\LARGE$\rightarrow$}}
\minipage{0.29\textwidth}
 \begin{center}
<<motivation_randforest, echo=FALSE, results=hide>>=
## Random Forest
for(i in 1:nobs) yforest[i] <- if(x[i]<0.27) 0.5 else { if(x[i]<0.39) 0.5 + 1.5*(plogis((x[i]-0.33)/6*700)) else 1+(1-plogis(kappa*(2*(x[i]-0.2)-1)))}
@
\visible<2->{
<<plot_motivation_randforest, fig=TRUE, echo=FALSE>>=
par(mar=c(2,0,2,0))
plot(x = x, y = y, xaxt="n", yaxt="n", ann=FALSE, col = "slategray", pch = 19)
box(lwd=5)
#lines(x = x, y = ytrue, col = "grey", lwd=5, main = "")
lines(x = x, y = yforest, col = pal["forest"], lwd=7, main = "")
@
}
\end{center}

\endminipage
\visible<3->{{\LARGE$\rightarrow$}}
\minipage{0.29\textwidth}
  \visible<3->{
  \begin{center}
  \begin{tikzpicture}
  \draw[line width=0.2mm, black] (0,0) rectangle (2.6,2.24);
  \node[rectangle, align=center] (sq) at (1.3, 1.12) {\Huge{?}};
  \end{tikzpicture}
  \end{center}}
\endminipage

\minipage{0.29\textwidth}
\begin{center}
\vspace{0.0cm}
\visible<1->{
Regression Tree\\
\vspace{0.5cm}
\resizebox{0.3\textwidth}{!}{
\begin{tikzpicture}
  \node[ellipse, fill=HighlightBlue!70, align=center] (n0) at (1, 2) {};
  \node[rectangle, fill=HighlightOrange!70, align=center] (n1) at (0.5, 1) {};
  \draw[-, line width=1pt] (n0) -- (n1);
  \node[ellipse, fill=HighlightBlue!70, align=center] (n2) at (1.5, 1) {};
  \draw[-, line width=1pt] (n0) -- (n2);
  \node[rectangle, fill=HighlightOrange!70, align=center] (n3) at (1, 0) {};
  \draw[-, line width=1pt] (n2) -- (n3);
  \node[rectangle, fill=HighlightOrange!70, align=center] (n4) at (2, 0) {};
  \draw[-, line width=1pt] (n2) -- (n4);
\end{tikzpicture}}
\vspace{0.3cm}\\
\code{rpart}\\
\code{party(kit)}\\
\vspace{1cm}}
\end{center}
\endminipage
\hspace{0.65cm}
\minipage{0.29\textwidth}
\begin{center}
\vspace{0.0cm}
\visible<2->{
Random Forest\\
\vspace{0.5cm}
\resizebox{0.9\textwidth}{!}{
\begin{tikzpicture}
  \node[ellipse, fill=HighlightBlue!70, align=center] (n00) at (1, 2) {};
  \node[rectangle, fill=HighlightOrange!70, align=center] (n01) at (0.5, 1) {};
  \draw[-, line width=1pt] (n00) -- (n01);
  \node[rectangle, fill=HighlightOrange!70, align=center] (n02) at (1.5, 1) {};
  \draw[-, line width=1pt] (n00) -- (n02);

@@

\subsection{Building Distributional Trees and Forests}
\begin{frame}
\frametitle{Building Distributional Trees and Forests}
{\bf Tree:}
\begin{enumerate}
\item Specify a distribution with log-likelihood function $\ell(\theta; y)$.
\item Estimate $\hat{\theta}$ via maximum likelihood.
\item Test for associations or instabilities of the scores $\frac{\partial \ell}{\partial \theta}(\hat{\theta};y_i)$ and each partitioning variable $x_i$.
%\item Assess whether the \emph{model scores} are associated with
%    (or change along) any of the available covariates -- e.g.,
%    using parameter instability tests (\emph{strucchange}) or
%    conditional inference (\emph{coin}).
\item Split the sample along the partitioning variable with the strongest association or instability.
    Choose breakpoint with highest improvement in log-likelihood.
\item Repeat steps 2--4 recursively in the subgroups
    until some stopping criterion is met.
    %-- e.g., for significance or sample size.
%\item Choose the variable with the strongest association
%\item Choose the split point which leads to the highest improvement of the model
%\item Split and repeat 2-6 in each node until a stopping criterion is met
\end{enumerate}

\vspace{0.4cm}
{\bf Forest:} Ensemble of trees.
\begin{itemize}
\item Bootstrap or subsamples.
\item Random input variable sampling.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Prediction}
%\vspace{1cm}
{\bf Tree:}\\
\begin{enumerate}
\item Select the subsample of the learning data which ends up in the same terminal node as the new observation.
\item Estimate $\hat{\theta}$ on this subsample.
\end{enumerate}
\vspace{0.5cm}

{\bf Forest:}\\
\begin{enumerate}
\item For each learning observation calculate a weight by counting the number of trees in which it ends up in the same terminal node as the new observation.
\item Estimate $\hat{\theta}$ on the weighted learning data.
\end{enumerate}
% but weighted by similarities of the learning data and the new observation over all trees
%\item Evaluate final node for new observation in each of the trees and investigate similarities with each of the learning observations
%\item Fit a distributional model for the new observation with different influences of the learning observations defined by weights
\end{frame}

\begin{frame}
\frametitle{Fitting a Tree}
\vspace*{-0.12cm}
\begin{center} 
DGP:  $\; Y\ |\ X = x \; \sim  \; \mathcal{N}(\mu(x), \sigma^2(x))$
\vspace*{-0.21cm}
<<dgp_tree, echo=FALSE, results=hide>>=
data <- data.frame(x = numeric(0), x = numeric(0), x = numeric(0))
names(data) <- c("x","x","x")
fig <- party(
  partynode(1L,
            split = partysplit(2L, breaks = 0.4),
            kids = list(
              partynode(2L, info = c(
                "n = 200",
                "   True parameters:   ",
                expression(mu == '4'),
                expression(sigma == '1')
              )),
              partynode(3L,
                        split = partysplit(3L, breaks = 0.8),
                        kids = list(
                          partynode(4L, info = c(
                            "n = 200",
                            "   True parameters:   ",
                            expression(mu == '12'),
                            expression(sigma == '3')
                          )),
                          partynode(5L, info = c(
                            "n = 100",
                            "   True parameters:   ",
                            expression(mu == '4'),
                            expression(sigma == '3')
                          )))))),
  data
)

@@

@@

@@

\begin{frame}[fragile]
\frametitle{Simulation}
\begin{center}
\vspace*{-1cm}
\setkeys{Gin}{width=0.8\linewidth}
<<plotsim_RMSE_par, fig=TRUE, echo=FALSE>>=
plot_rmse(simlist, type = "par")
@
\end{center}
\end{frame}

\begin{frame}[fragile]
\frametitle{Simulation}
\begin{center}
\vspace*{-1cm}
\setkeys{Gin}{width=0.8\linewidth}
<<plotsim_RMSE_exp, fig=TRUE, echo=FALSE>>=
plot_rmse(simlist, type = "exp")
@
\end{center}
\end{frame}

>>>>

\documentclass[11pt,t,usepdftitle=false,aspectratio=43]{beamer}
\usetheme[nototalframenumber, noslidenumber, url]{uibk}

\title{Distributional Regression Forests for Probabilistic Modeling and Forecasting}
\author{Lisa Schlosser, Torsten Hothorn, Heidi Seibold, Achim Zeileis}
\setbeamerfont{url}{size*={11.5pt}{13pt},series=\mdseries}
\URL{https://eeecon.uibk.ac.at/~zeileis/}
\headerimage{4}

@@

\begin{frame}[fragile]
\frametitle{Motivation}
\vspace{-0.41cm}
\begin{figure}[!htb]
\minipage{0.28\textwidth}
\begin{center}
<<motivation_GLM, echo=FALSE, results=hide>>=
nobs <- 200
## GLM
set.seed(7)
x <- c(1:nobs)/nobs
ytrue <- 1+x*1.5
y <- ytrue + rnorm(nobs,0,0.3)
@
\visible<2->{
<<plot_motivation_GLM, fig=TRUE, echo=FALSE>>=
par(mar=c(2,0,2,0))
plot(y=y , x=x, xaxt="n", yaxt="n", ann=FALSE, col = "slategray", pch = 19)
box(lwd=5)
lines(x = x, y = ytrue, col = pal["forest"], lwd = 7, main = "")
@
}
\end{center}
\endminipage
\visible<3->{{\LARGE$\rightarrow$}}
\minipage{0.28\textwidth}
\begin{center}
<<motivation_GAM, echo=FALSE, results=hide>>=
## GAM
set.seed(7)
x <- c(1:nobs)/nobs
x <- 2*(x-0.5)
ytrue <- x^3 
y <- ytrue + rnorm(nobs,0,0.3)
@
\visible<3->{
<<plot_motivation_GAM, fig=TRUE, echo=FALSE>>=
par(mar=c(2,0,2,0))
plot(y=y , x=x, xaxt="n", yaxt="n", ann=FALSE, col = "slategray", pch = 19)
box(lwd=5)
lines(x = x, y = ytrue, col = pal["forest"], lwd = 7, main = "")
@
}
\end{center}
\endminipage
\visible<4->{{\LARGE$\rightarrow$}}
\minipage{0.28\textwidth}
\begin{center}
<<motivation_GAMLSS, echo=FALSE, results=hide>>=
## GAMLSS
set.seed(7)
x <- c(1:nobs)/nobs
x <- 2*(x-0.5)
ytrue <- x^3
var <- exp(-(2*x)^2)/2
y <- ytrue + rnorm(nobs, 0, 0.1 + var)
@
\visible<4->{
<<plot_motivation_GAMLSS, fig=TRUE, echo=FALSE>>=
par(mar=c(2,0,2,0))
plot(x, y, xaxt = "n", yaxt = "n", ann = FALSE, type = "n")
polygon(c(x, rev(x)), c(ytrue + 0.1 + var, rev(ytrue - 0.1 - var)),
  col = pallight["forest"], border = "transparent")
lines(x, ytrue, col = pal["forest"], lwd=7)
points(x, y, col = "slategray", pch = 19)
box(lwd = 5)
@

@@

\begin{frame}[fragile]
\frametitle{Motivation}
\vspace{-0.2cm}
\begin{figure}[!htb]
\minipage{0.28\textwidth}
\begin{center}
<<motivation_regtree, echo=FALSE, results=hide>>=
## Reg. Tree
set.seed(7)
kappa <- 12
x <- c(1:nobs)/nobs
ytrue <- ytree <- yforest <- numeric(length = length(x))
for(i in 1:nobs) ytrue[i] <- if(x[i]<1/3) 0.5 else 1+(1-plogis(kappa*(2*(x[i]-0.2)-1)))
y <- ytrue + rnorm(nobs,0,0.3)
for(i in 1:nobs) ytree[i] <- if(x[i]<1/3) 0.5 else {if(x[i]<2/3) 2 else 1}
@
\visible<1->{
<<plot_motivation_regtree, fig=TRUE, echo=FALSE>>=
par(mar=c(2,0,2,0))
plot(x = x, y = y, xaxt="n", yaxt="n", ann=FALSE, col = "slategray", pch = 19)
box(lwd=5)
#lines(x = x, y = ytrue, col = "grey", lwd=5, main = "")
lines(x = x, y = ytree, col = pal["forest"], lwd=7)
@
}
\end{center}

\endminipage
\visible<2->{{\LARGE$\rightarrow$}}
\minipage{0.28\textwidth}
 \begin{center}
<<motivation_randforest, echo=FALSE, results=hide>>=
## Random Forest
for(i in 1:nobs) yforest[i] <- if(x[i]<0.27) 0.5 else { if(x[i]<0.39) 0.5 + 1.5*(plogis((x[i]-0.33)/6*700)) else 1+(1-plogis(kappa*(2*(x[i]-0.2)-1)))}
@
\visible<2->{
<<plot_motivation_randforest, fig=TRUE, echo=FALSE>>=
par(mar=c(2,0,2,0))
plot(x = x, y = y, xaxt="n", yaxt="n", ann=FALSE, col = "slategray", pch = 19)
box(lwd=5)
#lines(x = x, y = ytrue, col = "grey", lwd=5, main = "")
lines(x = x, y = yforest, col = pal["forest"], lwd=7, main = "")
@
}
\end{center}

\endminipage
\visible<3->{{\LARGE$\rightarrow$}}
\minipage{0.28\textwidth}
  \visible<3->{
  \begin{center}
  \begin{tikzpicture}
  \draw[line width=0.2mm, black] (0,0) rectangle (2.6,2.24);
  \node[rectangle, align=center] (sq) at (1.3, 1.12) {\Huge{?}};
  \end{tikzpicture}
  \end{center}}
\endminipage

\minipage{0.28\textwidth}
\begin{center}
\vspace{0.0cm}
\visible<1->{
Regression Tree\\
\vspace{0.5cm}
\resizebox{0.3\textwidth}{!}{
\begin{tikzpicture}
  \node[ellipse, fill=HighlightBlue!70, align=center] (n0) at (1, 2) {};
  \node[rectangle, fill=HighlightOrange!70, align=center] (n1) at (0.5, 1) {};
  \draw[-, line width=1pt] (n0) -- (n1);
  \node[ellipse, fill=HighlightBlue!70, align=center] (n2) at (1.5, 1) {};
  \draw[-, line width=1pt] (n0) -- (n2);
  \node[rectangle, fill=HighlightOrange!70, align=center] (n3) at (1, 0) {};
  \draw[-, line width=1pt] (n2) -- (n3);
  \node[rectangle, fill=HighlightOrange!70, align=center] (n4) at (2, 0) {};
  \draw[-, line width=1pt] (n2) -- (n4);
\end{tikzpicture}}
\vspace{0.3cm}\\
\code{rpart}\\
\code{party(kit)}\\
\vspace{1cm}}
\end{center}
\endminipage
\hspace{0.65cm}
\minipage{0.28\textwidth}
\begin{center}
\vspace{0.0cm}
\visible<2->{
Random Forest\\
\vspace{0.5cm}
\resizebox{0.9\textwidth}{!}{
\begin{tikzpicture}
  \node[ellipse, fill=HighlightBlue!70, align=center] (n00) at (1, 2) {};
  \node[rectangle, fill=HighlightOrange!70, align=center] (n01) at (0.5, 1) {};
  \draw[-, line width=1pt] (n00) -- (n01);
  \node[rectangle, fill=HighlightOrange!70, align=center] (n02) at (1.5, 1) {};
  \draw[-, line width=1pt] (n00) -- (n02);

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Fitting a Tree}
\vspace*{-0.12cm}
\begin{center} 
DGP:  $\; Y\ |\ X = x \; \sim  \; \mathcal{N}(\mu(x), \sigma^2(x))$
\vspace*{-0.21cm}
<<dgp_tree, echo=FALSE, results=hide>>=
data <- data.frame(x = numeric(0), x = numeric(0), x = numeric(0))
names(data) <- c("x","x","x")
fig <- party(
  partynode(1L,
            split = partysplit(2L, breaks = 0.4),
            kids = list(
              partynode(2L, info = c(
                "n = 200",
                "   True parameters:   ",
                expression(mu == '4'),
                expression(sigma == '1')
              )),
              partynode(3L,
                        split = partysplit(3L, breaks = 0.8),
                        kids = list(
                          partynode(4L, info = c(
                            "n = 200",
                            "   True parameters:   ",
                            expression(mu == '12'),
                            expression(sigma == '3')
                          )),
                          partynode(5L, info = c(
                            "n = 100",
                            "   True parameters:   ",
                            expression(mu == '4'),
                            expression(sigma == '3')
                          )))))),
  data
)

@@

\begin{frame}
\frametitle{Global likelihood estimation}
\begin{itemize}
\item Specified log-likelihood function $$\ell(\theta; y_i)$$ with distribution parameter $\theta$ and observation $y_i$ of a learning data set $\{y_i\}_{i = 1,\ldots,n}$.

\bigskip

\item Estimation of $\hat{\bold{\theta}}$ via maximum likelihood 
$$
\hat{\theta} = \max_{\theta \in \Theta} \sum_{i=1}^n \ell(\theta; y_i).
$$
%% equivalent to solving 
%% $$
%% \sum_{i=1}^n \frac{\partial \ell}{\partial \theta}(\hat{\theta}; y_i) = \sum_{i=1}^n s(y_i, \hat{\theta}) = 0.
%% $$
\end{itemize}

\begin{frame}
\frametitle{Adaptive local likelihood estimation}

$$
\hat{\theta}(\bold{x}) = \max_{\theta \in \Theta} \sum_{i=1}^n w_i(\bold{x}) \cdot \ell(\theta; y_i).
$$

Needed: Weights.

Via tree: 0/1.

Via forest: averaged across trees.

\subsection{Building Distributional Trees and Forests}
\begin{frame}
\frametitle{Building Distributional Trees and Forests}
{\bf Tree:}
\begin{enumerate}
\item Estimate $\hat{\theta}$ via maximum likelihood.
\item Test for associations or instabilities of the scores $\frac{\partial \ell}{\partial \theta}(\hat{\theta};y_i)$ and each partitioning variable $x_i$.
\item Split the sample along the partitioning variable with the strongest association or instability.
    Choose breakpoint with highest improvement in log-likelihood.
\item Repeat steps 1--3 recursively until some stopping criterion is met, yielding
    $B$ subgroups $\mathcal{B}_b$ with $b = 1, \dots, B$.
\end{enumerate}

\bigskip

{\bf Forest:} Ensemble of $T$ trees.
\begin{itemize}
\item Bootstrap or subsamples.
\item Random input variable sampling.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Adaptive local likelihood estimation}

{\bf Estimator:}
$$
\hat{\theta}(\bold{x}) =  \max_{\theta \in \Theta} \sum_{i=1}^n w_i(\bold{x}) \cdot \ell(\theta; y_i)
$$

\bigskip

\textbf{Weights:}

\begin{eqnarray*}
w^{\text{base}}_i(\bold{x})   & = & 1 \\[0.3cm]
w^{\text{tree}}_i(\bold{x})   & = & \sum_{b=1}^B I((\bold{x}_i \in \mathcal{B}_b) \land (\bold{x} \in \mathcal{B}_b)) \\[0.3cm]
w^{\text{forest}}_i(\bold{x}) & = & \frac{1}{T} \sum_{t=1}^T \sum_{b=1}^{B^t} I((\bold{x}_i \in \mathcal{B}^t_b) \land (\bold{x} \in \mathcal{B}^t_b))
\end{eqnarray*}

\begin{frame}
\frametitle{Simulation}

Overview

@@

\begin{frame}
\frametitle{Choosing a distribution}

\medskip
{\bf Based on:}
\begin{itemize}
\item Recommendations by subject matter literature.
\item Experiences from other modelling situations.
\item Common simplifications/generalizations/assumptions.
\end{itemize}

\bigskip
{\bf Examples:}
\begin{itemize}
\item Survival times: Weibull distribution, exponential distribution.
\item Wages, precipitation: censored normal distribution.
\item Temperature: normal distribution.
\item Count of events/accidents (insurance): Poisson distribution.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Alternative: Transformation model}

{\bf Distribution function:}
$$
F(y) = \Phi(\bold{a}_{Bs,d}(y)^\top \theta) 
$$

\begin{itemize} 
\item $\bold{a}_{Bs,d}(y)^\top \theta$ is a smooth, monotone Bernstein polynomial of degree $d$.
\item $d=1$ corresponds to $\mathcal{N}(\mu,\sigma^2)$.
\item $d=5$ is surprisingly flexible.
\end{itemize}

\textbf{Example:} Body Mass Index explained by lifestyle factors (Switzerland).

\begin{frame}
\frametitle{Alternative: Transformation model}

\vspace*{0.4cm}

\includegraphics[width=\textwidth]{cmpx-tree.pdf}

@@

%% \begin{frame}[fragile]
%% \frametitle{Simulation}
%% \begin{center}
%% \vspace*{-1cm}
%% \setkeys{Gin}{width=0.8\linewidth}
%% <<plotsim_RMSE_par, fig=TRUE, echo=FALSE>>=
%% plot_rmse(simlist, type = "par")
%% @
%% \end{center}
%% \end{frame}

%% \begin{frame}[fragile]
%% \frametitle{Simulation}
%% \begin{center}
%% \vspace*{-1cm}
%% \setkeys{Gin}{width=0.8\linewidth}
%% <<plotsim_RMSE_exp, fig=TRUE, echo=FALSE>>=
%% plot_rmse(simlist, type = "exp")
%% @
%% \end{center}
%% \end{frame}
